Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-17 write_up/mixfishsim_ecolmod_revisions.tex
Revisions per Coilin comments

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model ('MixFishSim`) incorporating: i) delay-difference population
dynamics, ii) population movement using Gaussian Random Fields to simulate
patchy, heterogeneously distributed \added{and moving fish} populations, and
iii) fishery dynamics for multiple fleet characteristics based on population
targeting under an explore-exploit strategy.\deleted{ This is implemented via a mix of
correlated random walk movement (for exploration) and learned behaviour (for
exploitation) phases of the fisheries. }\\ 
%%
\deleted{Fifty years of sub-daily fishing activity was simulated and used to
	draw inference on the underlying community structures. W}\added{We
	applied the framework to draw}\deleted{compared} inference\deleted{s}
\added{on community structure} \added{when using data generated from
}\deleted{based on}: commercial catch, a simulated fixed-site sampling survey
design and the true \added{(simulated)} underlying populations.
\deleted{W}\added{In doing so w}e \deleted{i)}establish the potential
limitations of fishery-dependent data in providing a robust picture of
spatiotemporal distributions\deleted{; and then ii) simulated an area closure
	based on areas defined from the different data sources at a range of
	temporal and spatial resolutions.}\deleted{Our framework allows users
	to explore the assumptions in modelling observational data and evaluate
	the underlying dynamics of such approaches at a fine spatial and
	temporal scale. In application to a mixed fishery exploiting four
	different populations w} \added{W}e found different spatial patterns
were evident and that the effectiveness of the spatial closure reduced when
data were aggregated across larger spatial areas. \deleted{; and then
	ii)}\added{We then simulated an area closure based on areas defined
	from the different data sources at a range of temporal and spatial
	resolutions.} Aggregation across time periods has less of a negative
impact on the closure success than over space.\deleted{ and w}\added{W}hile not
as effective as when based on on the true population, closures based on high
catch rates observed in commercial data were still able to reduce fishing on a
protected species. \\

\added{Our framework allows users to explore the assumptions in modelling
	observational data and evaluate the underlying dynamics of such
	approaches at a fine spatial and temporal scale. }\added{From our
	application w}\deleted{W}e conclude that commercial data, while
containing bias, provide a useful tool for managing catches in mixed fisheries
if applied at the correct spatiotemporal scale. \\
%%
\end{abstract}

@@

Fleet dynamics \replaced{were}{can be }broadly categorised into three
components. \textit{Fleet targeting} \replaced{determined}{determines} the
fleet catch efficiency and preference towards a particular population;
\textit{trip-level decisions} \replaced{determined}{that determines} the
initial location to be fished at the beginning of a trip; and
\textit{within-trip decisions}\replaced{determined fishing locations}{, that
	determines movement from one fishing spot to another} within a trip.
\replaced{This results in an explore-exploit strategy}{ was implemented in the
	model that combined these three components} for individual vessels to
maximise their catch from an unknown resource distribution \citep{Bailey2018}.
The decision to use an individual based model for fishing vessels was taken
because fishers are heterogeneous in their location choice behaviour due to
different objectives, risk preference and targeting preference
\citep{VanPutten2012a, Boonstra2015}.  Therefore fleet dynamics are emergent
from individual dynamics rather than pre-defined group dynamics.

@@

We consider that the increased availability of high resolution catch and
locational information from commercial fisheries will require it to be a key
source of data for ensuring management is implemented at the right scale in
future. For example, identifying hot-spots for bycatch reduction or identifying
spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
	Dedman2015, Ward2015}. Our simulation model has the potential to test
some of the assumptions behind the modelling approaches in identifying such
hotspots and indeed behind spatiotemporal modelling in general\replaced{,}{ (}e.g. comparing
GAMs, GLMMs, Random Forests and geostatistical models under different data
generation processes as exampled by \cite{Stock2019}\deleted{)}. \\

@@

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{[Colour] Data aggregation at different spatial resolutions
		over a ten year period. \added{The figure shows catch
			composition at each spatial unit represented by a
			square pie chart of the four populations. The area of
			each colour is proportionate to the weight of each
			population caught in that unit. Figure produced using
			the R package 'mapplots' (\cite{Gerritsen2014}.}
	}
	\label{fig:1}
\end{figure}

>>>>

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model ('MixFishSim`) incorporating: i) delay-difference population
dynamics, ii) population movement using Gaussian Random Fields to simulate
patchy, heterogeneously distributed \added{and moving fish} populations, and
iii) fishery dynamics for multiple fleet characteristics based on population
targeting under an explore-exploit strategy.\deleted{ This is implemented via a mix of
correlated random walk movement (for exploration) and learned behaviour (for
exploitation) phases of the fisheries. }\\ 
%%
\deleted{Fifty years of sub-daily fishing activity was simulated and used to
	draw inference on the underlying community structures. W}\added{We
	applied the framework to draw}\deleted{compared} inference\deleted{s}
\added{on community structure} \added{when using data generated from
}\deleted{based on}: commercial catch, a simulated fixed-site sampling survey
design and the true \added{(simulated)} underlying populations.
\deleted{W}\added{In doing so w}e \deleted{i)}establish the potential
limitations of fishery-dependent data in providing a robust picture of
spatiotemporal distributions\deleted{; and then ii) simulated an area closure
	based on areas defined from the different data sources at a range of
	temporal and spatial resolutions.}\deleted{Our framework allows users
	to explore the assumptions in modelling observational data and evaluate
	the underlying dynamics of such approaches at a fine spatial and
	temporal scale. In application to a mixed fishery exploiting four
	different populations w} \added{W}e found different spatial patterns
were evident and that the effectiveness of the spatial closure reduced when
data were aggregated across larger spatial areas. \deleted{; and then
	ii)}\added{We then simulated an area closure based on areas defined
	from the different data sources at a range of temporal and spatial
	resolutions.} Aggregation across time periods has less of a negative
impact on the closure success than over space. \deleted{ and w}\added{W}hile not
as effective as when based on on the true population, closures based on high
catch rates observed in commercial data were still able to reduce fishing on a
protected species. \\ 
%%
\added{Our framework allows users to explore the assumptions in modelling
	observational data and evaluate the underlying dynamics of such
	approaches at a fine spatial and temporal scale. From our application
	w}\deleted{W}e conclude that commercial data, while containing bias,
provide a useful tool for managing catches in mixed fisheries if applied at the
correct spatiotemporal scale. \\
%%
\end{abstract}

@@

Fleet dynamics \replaced{were}{can be }broadly categorised into three
components. \textit{Fleet targeting} \replaced{determined}{determines} the
fleet catch efficiency and preference towards a particular population;
\textit{trip-level decisions} \replaced{determined}{that determines} the
initial location to be fished at the beginning of a trip; and
\textit{within-trip decisions} \replaced{determined fishing locations}{, that
	determines movement from one fishing spot to another} within a trip.
\replaced{This results in an explore-exploit strategy}{ was implemented in the
	model that combined these three components} for individual vessels to
maximise their catch from an unknown resource distribution \citep{Bailey2018}.
The decision to use an individual based model for fishing vessels was taken
because fishers are heterogeneous in their location choice behaviour due to
different objectives, risk preference and targeting preference
\citep{VanPutten2012a, Boonstra2015}.  Therefore fleet dynamics are emergent
from individual dynamics rather than pre-defined group dynamics.

@@

We consider that the increased availability of high resolution catch and
locational information from commercial fisheries will require it to be a key
source of data for ensuring management is implemented at the right scale in
future. For example, identifying hot-spots for bycatch reduction or identifying
spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
	Dedman2015, Ward2015}. Our simulation model has the potential to test
some of the assumptions behind the modelling approaches in identifying such
hotspots and indeed behind spatiotemporal modelling in general\replaced{, }{
	(}e.g. comparing GAMs, GLMMs, Random Forests and geostatistical models
under different data generation processes as exampled by
\cite{Stock2019}\deleted{)}. \\

@@

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{[Colour] Data aggregation at different spatial resolutions
		over a ten year period. \added{The figure shows catch
			composition at each spatial unit represented by a
			square pie chart of the four populations. The area of
			each colour is proportional to the weight of each
			population caught in that unit. Figure produced using
			the R package 'mapplots' (\cite{Gerritsen2014}.}
	}
	\label{fig:1}
\end{figure}
